---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rschtasks

<!-- badges: start -->
<!-- badges: end -->

The goal of rschtasks is to make it easier to created scheduled tasks on a Windows machine in R.

## Installation

You can install the development version of rschtasks from [Github](https://github.com/jmbarbone/rschtasks)

``` r
remotes::install_github("jmbarbone/rschtasks")
```

## Examples

```{r}
library(rschtasks)
```

Create an object with the task parameters.
This includes several checks to make sure the tasks are set up properly, with a few additional features.

```{r R6 example}
task <- TaskScheduler$new(
  task_name  = "open notepad",
  task_run   = "notepad",
  schedule   = "once",
  start_time = "now",
  quiet      = TRUE,
  force      = TRUE
)
```

With the task you can run commands and see the results and calls.
The task object can be reused.

```{r R6 example tasks}
task$create()
task$result
task$system_call

task$show_sid()
task$result
task$system_call

task$delete()
task$result
task$system_call
```

Alternatively, wrappers are provided and can be used instead.

```{r example}
schtasks_create(
  "open notepad",
  task_run = "notepad",
  schedule = "once",
  start_time = "asap"
)
schtasks_showsid("open notepad")
schtasks_delete("open notepad", force = TRUE)
```


## See also

[taskscheduleR](https://github.com/bnosac/taskscheduleR), available on [CRAN](https://CRAN.R-project.org)

